---
title: "Should I Ask Myself"
author: "Orkun Gokhan, Ozgur Oney, Yusuf Tiryaki"
output:
  html_document: default
  html_notebook: default
---


# Inroduction
## Background
You are a busy and hardworking metropol citizen! 
Long working hours and too much time wasted on traffic!
There is no time and suitable environment to meet a romantic partner!
Speed Dating Events is a popular match making activity in these days if you agree with all above.<br>

During the events, the attendees would have a four minute "first date" with every other participant of the opposite sex. At the end of their four minutes, participants were asked if they would like to see their date again. They were also asked to rate their date on six attributes: Attractiveness, Sincerity, Intelligence, Fun, Ambition, and Shared Interests.
<br>
<br>
During analysis we are going to achieve some descriptive analysis about how participants describe themselves and how their partners voted them. 
We are going to ask the question "If we decide the postive responses of participants just considering how they describe themselves, does it make sense?" and try find outcomes which help us to answer this question


## Data Set
The data set was gathered from speed dating events from 2002-2004. The research was carried out by Columbia Business School professors Ray Fisman and Sheena Iyengar as basis for their paper “Gender Differences in Mate Selection: Evidence From a Speed Dating Experiment”. The dataset also includes questionnaire data gathered from participants at different points in the process. These fields include: demographics, dating habits, self-perception across key attributes, beliefs on what others find valuable in a mate, and lifestyle information<br>
In Dataset:<br>
8368 records<br>
278 Male participant<br>
276 Female participant<br>

# Data Cleaning And Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
knitr::opts_chunk$set(out.width='900px', dpi=200)
#install packages if necessary
if (!require("pacman")) install.packages("pacman")
  pacman::p_load("scales","ggplot2","dplyr","reshape2","grid","gridExtra","devtools","GGally")

# thanks to ricardo
if (!require(ggradar))
  devtools::install_github("ricardo-bion/ggradar", 
                          dependencies=TRUE) 

#if(!exists("IFDEF_DEGPG_UTILS"))
#  source("Utils.R")

rawdat <- 
read.csv('./data/Speed Dating Data.csv', header = T, stringsAsFactors = F)
```

Transform gender field to a more reable format 0/1 -> Female/Male and make it factor
```{r tranformations, echo = FALSE}
data.transformed <- rawdat
#Cinsiyeti daha okunur yapalım
data.transformed[rawdat$gender == 0,]$gender <- 'Female'
data.transformed[rawdat$gender == 1,]$gender <- 'Male'
data.transformed$gender <- as.factor(data.transformed$gender)
```
Remove records which have no id and partnerid
```{r data clean, echo = FALSE}
#id yada partner id olmayanları çıkar
data.cleaned <-
data.transformed %>%
  filter(!pid == "NA" | !id =="NA")
```

Create a new data frame which is a subset of cleaned and only contains considered columns
```{r data selection, echo = FALSE}
#sadece kullanacağımız attribute'ları alalım
data.analyse <-
data.cleaned %>%
  select(iid,pid, gender, attr3_1, sinc3_1, intel3_1, fun3_1, amb3_1, attr5_1, sinc5_1, intel5_1, fun5_1, amb5_1, attr, sinc, intel, fun, amb, shar,attr_o, sinc_o, intel_o, fun_o, amb_o, shar_o,dec_o,dec)
#sadece ikinci analiz için kullanacağımız farkları alalım
data.analyse2 <-
  data.cleaned %>%
  select(iid,pid, gender, samerace ,match ,age,race_o ,race ,imprace, goal, date ,career_c ,numdat_2 , match_es , satis_2,you_call,them_cal)
#sadece üçüncü analiz için kullanacağımız farkları alalım
age.difference.subgroup <- data.transformed %>%
  group_by(age, age_o) %>%
  summarise(
    n.people = n(), 
    n.matches = sum(match)
  ) %>%
  filter(!is.na(age) & !is.na(age_o))
# geçici tabloları temizleyelim
rm(data.transformed,data.cleaned)

```

```{r compile data, echo=FALSE}
data.others.yourself.partners <-
  data.analyse %>% 
  group_by(iid) %>% 
  summarise(
    Gender = first(gender),
    PositiveResponseScore = mean(dec_o, na.rm = TRUE),
    Attractive.Others = first(attr5_1), 
    Sincere.Others = first(sinc5_1), 
    Intelligent.Others = first(intel5_1), 
    Fun.Others = first(fun5_1), 
    Ambitious.Others = first(amb5_1), 
    Attractive.Yourself = first(attr3_1), 
    Sincere.Yourself = first(sinc3_1), 
    Intelligent.Yourself = first(intel3_1), 
    Fun.Yourself = first(fun3_1), 
    Ambitious.Yourself = first(amb3_1),
    Attractive.Partners = mean(attr_o, na.rm = TRUE), 
    Sincere.Partners = mean(sinc_o, na.rm = TRUE), 
    Intelligent.Partners = mean(intel_o, na.rm = TRUE), 
    Fun.Partners = mean(fun_o, na.rm = TRUE), 
    Ambitious.Partners = mean(amb_o, na.rm = TRUE))

#GGally::ggpairs(data = data.others.yourself.partners)
```

# Analysis
## How measure yourself
This question about participants themselves. Every participant scores a 1-10 point for each attribute.
So we can see how people think about themselves.

### Measure yourself(Population mean)
Let's how a look how pariticipants think about themselves on avarage
```{r how  measure yourself mean, echo = FALSE}
data.measure.yourself.mean <-
  data.others.yourself.partners %>% 
  filter(!is.na(Attractive.Yourself)) %>%
  group_by(Gender) %>% 
  summarise(Attractive = mean(Attractive.Yourself), Sincere = mean(Sincere.Yourself), Intelligent = mean(Intelligent.Yourself), Fun = mean(Fun.Yourself), Ambitious = mean(Ambitious.Yourself))

plot.measure.yourself.mean.all <- ggradar(plot.data = data.measure.yourself.mean, grid.mid = 5, grid.max = 10, legend.title = "Gender", grid.label.size =3,axis.label.size=4 )
plot.measure.yourself.mean.all
```

### Measure yourself distribution
```{r how  measure yourself, echo = FALSE}

plot.measure.yourself <- ggplot(data = data.others.yourself.partners) + coord_flip()

plot.measure.yourself.attractive <- plot.measure.yourself + geom_boxplot(mapping = aes(x = Gender, y = Attractive.Yourself)) + labs(y="Attractiveness", x ="Gender", title = "How Attractive Are You?")

plot.measure.yourself.ambitious <- plot.measure.yourself + geom_boxplot(mapping = aes(x = Gender, y = Ambitious.Yourself)) + labs(y="Ambitious", x ="Gender", title = "How Ambitious Are You?")

plot.measure.yourself.sincere <- plot.measure.yourself + geom_boxplot(mapping = aes(x = Gender, y = Sincere.Yourself)) + labs(y="Sincere", x ="Gender", title = "How Sincere Are You?")

plot.measure.yourself.intelligent <- plot.measure.yourself + geom_boxplot(mapping = aes(x = Gender, y = Intelligent.Yourself)) + labs(y="Intelligent", x ="Gender", title = "How Intelligence Are You?")


plot.measure.yourself.fun <- plot.measure.yourself + geom_boxplot(mapping = aes(x = Gender, y = Fun.Yourself)) + labs(y="Fun", x ="Gender", title = "How Fun Are You?")


grid.arrange(plot.measure.yourself.attractive, plot.measure.yourself.ambitious, plot.measure.yourself.sincere, plot.measure.yourself.intelligent, plot.measure.yourself.fun, ncol = 1)

```
Ambitious and Fun disitribitions are look like normally distributed but others have upper or lower quartile medians. Data has high density points in these quartiles. So using median is more meaningfull to describe these features.

### Measure yourself Median
According to distribution properties median value is more descriptive than mean.
```{r how  measure yourself median, echo = FALSE}
#median daha açıklayıcı
data.measure.yourself.median <-
  data.others.yourself.partners %>% 
  filter(!is.na(Attractive.Yourself)) %>%
  group_by(Gender) %>% 
  summarise(Attractive = median(Attractive.Yourself), Sincere = median(Sincere.Yourself), Intelligent = median(Intelligent.Yourself), Fun = median(Fun.Yourself), Ambitious = median(Ambitious.Yourself)) 
plot.measure.yourself.median.all <- ggradar(plot.data = data.measure.yourself.median, grid.mid = 5, grid.max = 10, legend.title = "Gender", grid.label.size =3,axis.label.size=4 )
plot.measure.yourself.median.all
```
Famales describe themselves more Sincere than males and males describe themselves more Intelligent but for other features it look likes that there is no gender effect.
All the features are have upper values than %50 as radar chart says, there is no anomolies for any feature.

## How others perceive you
This question is about 'the others'. All we have a 'the others' concept in our mind so lets listen some statistics about it.

### How others perceive you(Population Mean)
```{r how  other percieve mean, echo = FALSE}
data.other.percieve.mean <-
  data.others.yourself.partners %>% 
  filter(!is.na(Attractive.Others)) %>%
  group_by(Gender) %>% 
  summarise(Attractive = mean(Attractive.Others), Sincere = mean(Sincere.Others), Intelligent = mean(Intelligent.Others), Fun = mean(Fun.Others), Ambitious = mean(Ambitious.Others))

plot.other.percieve.mean.all <- ggradar(plot.data = data.other.percieve.mean, grid.mid = 5, grid.max = 10, legend.title = "Gender", grid.label.size =3,axis.label.size=4)
plot.other.percieve.mean.all
```

### How others perceive you distribution 
```{r how  other percieve, echo = FALSE}
plot.other.percieve <- ggplot(data = data.others.yourself.partners) +  coord_flip()

plot.other.percieve.attractive <- plot.other.percieve + geom_boxplot(mapping = aes(x = Gender, y = Attractive.Others)) + labs(y="Attractiveness", x ="Gender", title = "How Attractive Are You By Others?")

plot.other.percieve.ambitious <- plot.other.percieve + geom_boxplot(mapping = aes(x = Gender, y = Ambitious.Others)) + labs(y="Ambitious", x ="Gender", title = "How Ambitious Are You By Others?")

plot.other.percieve.sincere <- plot.other.percieve + geom_boxplot(mapping = aes(x = Gender, y = Sincere.Others)) + labs(y="Sincere", x ="Gender", title = "How Sincere Are You By Others?")

plot.other.percieve.intelligent <- plot.other.percieve + geom_boxplot(mapping = aes(x = Gender, y = Intelligent.Others)) + labs(y="Intelligent", x ="Gender", title = "How Intelligence Are You By Others?")

plot.other.percieve.fun <-plot.other.percieve + geom_boxplot(mapping = aes(x = Gender, y = Fun.Others)) + labs(y="Fun", x ="Gender", title = "How Fun Are You By Others?")

grid.arrange(plot.other.percieve.attractive, plot.other.percieve.ambitious, plot.other.percieve.sincere, plot.other.percieve.intelligent, plot.other.percieve.fun, ncol = 1 )

```

### How others perceive you(Population Median) 
```{r how  other percieve median, echo = FALSE}
# median mean'den daha açıklayıcı görünüyor
data.other.percieve.median <-
  data.others.yourself.partners %>% 
  filter(!is.na(Attractive.Others)) %>%
  group_by(Gender) %>% 
  summarise(Attractive = median(Attractive.Others), Sincere = median(Sincere.Others), Intelligent = median(Intelligent.Others), Fun = median(Fun.Others), Ambitious = median(Ambitious.Others))

plot.other.percieve.median.all <- ggradar(plot.data = data.other.percieve.median, grid.mid = 5, grid.max = 10, legend.title = "Gender", grid.label.size =3,axis.label.size=4)
plot.other.percieve.median.all

```
People change their mind when we ask how others think about you in the field Sincere, Intelligent and Fun.
When measuring themselves females have more Sincere points but they think same with males when 'the others' effect asked. Intelligence is the same issue for males.
Fun feature is interesting beacuse females and males differ in this case either they think same when there is no the others effect

## The others and yourself?
Is it possible to say measuring yourself and deciding about how others think about you has a relationship?
We measure ourselves without considering how others perceive us or vice versa?
Lets have some statistics
```{r are we same test,echo = FALSE}
#measure yourself and other percieve sorularını cevaplayanlar
data.others.yourself <-
  data.others.yourself.partners %>% 
  filter(!is.na(Attractive.Others)&!is.na(Attractive.Yourself))



plot.others.yourself <- ggplot(data = data.others.yourself) + geom_jitter(alpha = 0.2) + geom_smooth(method = "lm") + scale_x_continuous(breaks = seq(0,10,1)) + theme(panel.background = element_blank())
#aynı populasyon mu için t-paiared test
t.test(data.others.yourself$Attractive.Yourself, data.others.yourself$Attractive.Others, paired=TRUE) -> t.others.yourself.attractive
t.others.yourself.attractive
cor.test(data = data.others.yourself, ~Attractive.Yourself+Attractive.Others) -> cor.others.yourself.attractive
cor.others.yourself.attractive
plot.others.yourself.attractive <- plot.others.yourself + aes(x = Attractive.Yourself, y = Attractive.Others) + annotate("text", x = 7, y = 1, label = paste("Cor = ",round(cor.others.yourself.attractive$estimate,digits = 4) )) +
annotate("text", x = 7, y = 2, label = paste("T-paired = ",round(t.others.yourself.attractive$p.value, digits = 4) ))
plot.others.yourself.attractive

t.test(data.others.yourself$Ambitious.Yourself, data.others.yourself$Ambitious.Others, paired=TRUE)-> t.others.yourself.ambitious
t.others.yourself.ambitious
cor.test(data = data.others.yourself, ~Ambitious.Yourself+Ambitious.Others) -> cor.others.yourself.ambitious
cor.others.yourself.ambitious
plot.others.yourself.ambitious <- plot.others.yourself + aes(x = Ambitious.Yourself, y = Ambitious.Others) + annotate("text", x = 7, y = 1, label = paste("Cor = ",round(cor.others.yourself.ambitious$estimate,digits = 4) )) +
annotate("text", x = 7, y = 2, label = paste("T-paired = ",round(t.others.yourself.ambitious$p.value, digits = 4) ))
plot.others.yourself.ambitious

t.test(data.others.yourself$Sincere.Yourself, data.others.yourself$Sincere.Others, paired=TRUE)-> t.others.yourself.sincere
t.others.yourself.sincere
cor.test(data = data.others.yourself, ~Sincere.Yourself+Sincere.Others) -> cor.others.yourself.sincere
cor.others.yourself.sincere
plot.others.yourself.sincere <- plot.others.yourself + aes(x = Sincere.Yourself, y = Sincere.Others) + annotate("text", x = 7, y = 1, label = paste("Cor = ",round(cor.others.yourself.sincere$estimate,digits = 4) )) +
annotate("text", x = 7, y = 2, label = paste("T-paired = ",round(t.others.yourself.sincere$p.value, digits = 4) ))
plot.others.yourself.sincere

t.test(data.others.yourself$Intelligent.Yourself, data.others.yourself$Intelligent.Others, paired=TRUE)-> t.others.yourself.intelligent
t.others.yourself.intelligent
cor.test(data = data.others.yourself, ~Intelligent.Yourself+Intelligent.Others) -> cor.others.yourself.intelligent
cor.others.yourself.intelligent
plot.others.yourself.intelligent <- plot.others.yourself + aes(x = Intelligent.Yourself, y = Intelligent.Others) + annotate("text", x = 7, y = 1, label = paste("Cor = ",round(cor.others.yourself.intelligent$estimate,digits = 4) )) +
annotate("text", x = 7, y = 2, label = paste("T-paired = ",round(t.others.yourself.intelligent$p.value, digits = 4) ))
plot.others.yourself.intelligent

t.test(data.others.yourself$Fun.Yourself, data.others.yourself$Fun.Others, paired=TRUE)-> t.others.yourself.fun
t.others.yourself.fun
cor.test(data = data.others.yourself, ~Fun.Yourself+Fun.Others) -> cor.others.yourself.fun
cor.others.yourself.fun
plot.others.yourself.fun <- plot.others.yourself + aes(x = Fun.Yourself, y = Fun.Others) + annotate("text", x = 7, y = 1, label = paste("Cor = ",round(cor.others.yourself.fun$estimate,digits = 4) )) +
annotate("text", x = 7, y = 2, label = paste("T-paired = ",round(t.others.yourself.fun$p.value, digits = 4) ))
plot.others.yourself.fun


grid.arrange(plot.others.yourself.attractive, plot.others.yourself.ambitious, plot.others.yourself.sincere, plot.others.yourself.intelligent, plot.others.yourself.fun)

```
We divide the set two experiment groups 'Measure Yourself' and 'How others percieve you'. Participants of each group are same so we have the chance to apply a T-Paired test. 
T-Paired test can say us if particapants are same person when they are talking about features as themselves and as others view?
All the features have strong positive correlations. If a person believe that he/she is attractive then nearly sure others will percieve he/she attractive.
Having a conclusion using T-paired test statistics is really difficult. For Ambitious it is 1 which means nobody changes their mind with the others effect but for Sincire attribute everybody changes their mind.
May be values are not suitable for a T-Paired test beacuse we know that paticipants give points in discerete scale which is 1 to 10 so there is no option to give 5.2 point result can differ in categorical manner.


## How measure yourself and how others percieve you
```{r are we same, echo = FALSE}
grid.arrange(plot.measure.yourself.median.all, plot.other.percieve.median.all, ncol = 1)
```
 


# Meet with your partners
Now we are ready to get objective evaluations from the real 'the others'. Every participant assessed his/her partners and here we are with results.

## Measure yourself and Partners evaluations
```{r market value, echo = FALSE}
data.partners.mean <-
  data.others.yourself.partners %>% 
  filter(!is.na(Attractive.Partners)&!is.na(Sincere.Partners)&!is.na(Intelligent.Partners)&!is.na(Fun.Partners)&!is.na(Ambitious.Partners)) %>%
  group_by(Gender) %>% 
  summarise(Attractive = mean(Attractive.Partners), Sincere = mean(Sincere.Partners), Intelligent = mean(Intelligent.Partners), Fun = mean(Fun.Partners), Ambitious = mean(Ambitious.Partners))

plot.partners.mean.all <- ggradar(plot.data = data.partners.mean , grid.mid = 5, grid.max = 10, legend.title = "Gender", grid.label.size =3,axis.label.size=4 )
plot.partners.mean.all

data.yourself.partners <-
   data.others.yourself.partners %>% 
  filter(!is.na(Attractive.Partners)&!is.na(Sincere.Partners)&!is.na(Intelligent.Partners)&!is.na(Fun.Partners)&!is.na(Ambitious.Partners))


#cor.test(data = data.yourself.partners,  ~Attractive.Yourself+Attractive.Partners)
#cor.test(data = subset(data.yourself.partners, Gender == 'Male'),  ~Attractive.Yourself+Attractive.Partners)
#cor.test(data = subset(data.yourself.partners, Gender == 'Female'),  ~Attractive.Yourself+Attractive.Partners)

plot.yourself.partners <- ggplot(data = data.yourself.partners) + geom_point(position = "jitter", alpha = 1/2) +  facet_wrap(~Gender) + geom_smooth(method = lm) + scale_x_continuous(breaks = seq(0,10,2)) + scale_y_continuous(breaks = seq(0,10,2))

plot.yourself.partners.attractive <- plot.yourself.partners  + aes(x = Attractive.Yourself, y = Attractive.Partners)
plot.yourself.partners.ambitious <- plot.yourself.partners  + aes(x = Ambitious.Yourself, y = Ambitious.Partners)  
plot.yourself.partners.sincere <- plot.yourself.partners  + aes(x = Sincere.Yourself, y = Sincere.Partners)
plot.yourself.partners.intelligent <- plot.yourself.partners  + aes(x = Intelligent.Yourself, y = Intelligent.Partners)
plot.yourself.partners.fun <- plot.yourself.partners  + aes(x = Fun.Yourself, y = Fun.Partners)

grid.arrange(plot.yourself.partners.attractive, plot.yourself.partners.ambitious, plot.yourself.partners.sincere, plot.yourself.partners.intelligent, plot.yourself.partners.fun)

```
Scatter plots are for participants self measurements and actual scores by partners. We can see that there is not too much relationship between how participant describe himself/herself and  his/her partners describe him/her.
Just for males it looks like if they think they are attractive  also their partners think they are attractive.

## Positive response score by gender
```{r decision score by gender, echo = FALSE}
data.score.yourself.partners.all <- data.others.yourself.partners
data.score.yourself.partners.males <- data.score.yourself.partners.all %>% filter(Gender == 'Male')
data.score.yourself.partners.females <- data.score.yourself.partners.all %>% filter(Gender == 'Female')

ggplot(data = data.score.yourself.partners.all) + geom_histogram(mapping = aes(x = PositiveResponseScore,fill = Gender), binwidth = 0.02) + facet_wrap(~Gender)
```
Positive response score distribution looks like uniform. For males it is more right screwed which means high score males less common. For females it looks like a perfect uniform distribution.
For population on avarage; a participant thinks half of his/her partners are ideal romantic candidates for him/her

## Which features are important to get a positive response?
```{r most positive features, echo = FALSE}
plot.score.partners <- ggplot(data = data.score.yourself.partners.all, mapping = aes(x = PositiveResponseScore, color = Gender))  + geom_point(alpha = 1/2) +   geom_smooth(method = lm, se = F)

plot.score.partners.attractive <- plot.score.partners + aes(y = Attractive.Partners)
plot.score.partners.ambitious <- plot.score.partners + aes(y = Ambitious.Partners)
plot.score.partners.sincere <- plot.score.partners + aes(y = Sincere.Partners)
plot.score.partners.intelligent <- plot.score.partners + aes(y = Intelligent.Partners)
plot.score.partners.fun <- plot.score.partners + aes(y = Fun.Partners)

grid.arrange(plot.score.partners.attractive, plot.score.partners.ambitious, plot.score.partners.sincere, plot.score.partners.intelligent, plot.score.partners.fun)

```
Most correlated attributes are Attractive and Fun. If a participant find his/her partner attractive it is very common to decide it is a ideal romantic partner and it is same for both gender.



## If just ask participant?
```{r most positive features experiment , echo = FALSE}
fit <- lm(PositiveResponseScore ~ Attractive.Partners + Fun.Partners, data = subset(data.score.yourself.partners.all, !is.na(Attractive.Yourself)))
summary(fit)
data.estimation <- data.others.yourself.partners %>% select(Attractive.Yourself, Fun.Yourself, PositiveResponseScore, Gender, Attractive.Partners)  %>% filter(!is.na(Attractive.Yourself))

names(data.estimation) <- c("Attractive.Partners", "Fun.Partners","Score.Actual","Gender","Attractive.Actual")
modelEstimate = predict(fit, newdata = data.estimation,
                        interval="prediction", level = .95)

data.estimation$Score.Estimated <- modelEstimate[,1]
ggplot(data = data.estimation, mapping = aes(x = Score.Actual, y = Score.Estimated,color = Gender)) + geom_point() + scale_y_continuous(breaks = seq(0,1,0.25))
```
This is a simple experiment to see what will be difference if we decide just asking participants about themselves. We took the most signicifant attributes ('Attractive', 'Fun') and build a linear model to estimate positive response rate.
Actually this is not a menaingfull statistical method, it just for fun :)
Result plot tells us answers to 'Measure yourself' questions is not related romantic partner matching. 


## Other perspectives
We have focused on attributes of people recently, from now on we are going to check what other attributes are;

At the beginning we reshape our datasets

```{r data reshape, echo = FALSE}
data.goalrace <-
  data.analyse2 %>% 
  group_by(iid) %>% 
  summarise(
    Gender = first(gender),
    Samerace = first(samerace),
    Match = first(match),
    Race= first(race),
    PartnerRace= first(race_o),
    imprace = first(imprace), 
    Goal = mean(goal, na.rm = TRUE),
    CareerOpp = first(career_c),
    EstMatch = first(match_es),
    YouCall = mean(you_call, na.rm = TRUE),
    ThemCall = mean(them_cal, na.rm = TRUE))
```
After that we choose only four column to make our analyse easier

### Is there any relation between goals and set up a dates?

```{r defined New Data for Goal Analyse , echo = FALSE}
#Hedefi görebilmek adına yeni data seti oluşturduk
data.goal <-
  data.analyse2 %>% 
  group_by(iid) %>% 
  summarise(
    Gender = first(gender),
    match = first(match),
    YouCall = mean(you_call, na.rm = TRUE),
    ThemCall = mean(them_cal, na.rm = TRUE),
    Goal = mean(goal, na.rm = TRUE))
```
Defined goals with explanation as Speed Dating Data Key
```{r defined goals in words , echo = FALSE}
#Hedefin data içerisinde yer almayan anlamlarını ekledik

data.gname <- data.goal
#Eşleşmeleri açalım
data.gname[data.goal$Goal == '1',]$Goal <- 'Fun Night Out'
data.gname[data.goal$Goal == '2',]$Goal <- 'Meet New People'
data.gname[data.goal$Goal == '3',]$Goal <- 'To Get Date'
data.gname[data.goal$Goal == '4',]$Goal <- 'Serius Relation'
data.gname[data.goal$Goal == '5',]$Goal <- 'to say I did'
data.gname[data.goal$Goal == '6',]$Goal <- 'other'
data.gname[data.goal$Goal == 'NaN',]$Goal <- 'other'
data.gname$Goal <- as.factor(data.gname$Goal)
```

Our data includes two fields; 
youcall= How many partners you have contacted to set up a date?
themcall= How many partners have contacted with you?

We want to prove the effect of goals for setting up a date

```{r graphs for goals of people , echo = FALSE}

##Kişilerin geliş amacına göre eşleşme çağrılarının gösterimi
ggplot(data = data.gname) + geom_histogram(stat="identity",mapping = aes(x = Goal, y=YouCall, fill = Gender)) + ggtitle("You-Gender")+ theme(axis.title=element_text(face="bold.italic",size="12", color="brown"), legend.position="top")

##Kişilerin geliş amacına göre onlarla iletişime geçen diğer kişilerin gösterimi
ggplot(data = data.gname) + geom_histogram(stat="identity",mapping = aes(x = Goal, y=ThemCall, fill = Gender)) + ggtitle("Them-Gender")+ theme(axis.title=element_text(face="bold.italic",size="12", color="brown"), legend.position="top")
##Total Görünüm
ggplot(data = data.gname) + geom_histogram(stat="identity",mapping = aes(x = Goal, y=ThemCall+YouCall, fill = Gender)) + ggtitle("TotalCall-Gender")+ theme(axis.title=element_text(face="bold.italic",size="12", color="brown"), legend.position="top")
```

Most of people (who have a match) comes speed dating for two reason "Fun Night Out and Meet New People"

There is a domination of men to contacted set up a date(in your gender graph), and there is a domination of women to have request for set up a date. 

As an interesting point some people join speed dating just to say "i did it". Mostly they don't want to contacted anybody, but all of them have contacted with their partners. So if you are not interested with other people, they try to impress you more!


### What people think about Race?
There are lots of questions in our analysis about Race, we have a race of people, race of their partner and their opinion about matching with same and different race(imprace).

First of all, we want to explain what is imprace?
People who want to match with the same race, they choose close to 10 in our model. If the race is not important for them, they choose close to 1.

Transform samerace field to a more reable format 0/1 -> Diff Race Match /Same Race Match and make it factor 
```{r graph of race and match, echo = FALSE}

#Okunur olması adına Irk eşlemesini detaylandırdık
data.goalrace <- data.goalrace
#Eşleşmeleri açalım
data.goalrace[data.goalrace$Samerace == 0,]$Samerace <- 'Diff Race Match'
data.goalrace[data.goalrace$Samerace == 1,]$Samerace <- 'Same Race Match'
data.goalrace$Samerace <- as.factor(data.goalrace$Samerace)
#Samerace detayına göre iki grafik çizdirerek insanların aynı ırkta olmaya verdiği önem ile aynı ırktan gerçekleşen eşleşme durumlarını karşılaştırdık
ggplot(data = data.goalrace) + geom_histogram(mapping = aes(x = imprace, fill = Gender), binwidth = 1) + facet_wrap(~Samerace) + ggtitle("Race Effect")+  theme(axis.title=element_text(face="bold.italic",size="12", color="red"), legend.position="top") 

```
So we have a figure to count match numbers of people in 2 graph with effect of imprace.

In same race match graph, we can see most of the people doesn't believe the effect of race in their selection. But we can see they all match with the same race, so they have prejudice to choose someone in their subconscious.
For the good news, some people say I am totally against on relationships with a different race. After speed dating they found somebody to change their idea. But it's a really small group. 


### Is there any effects on age gap?

Age difference between partners has long been a question of interest. Research on age difference in couples suggests that while the desired gap for men and women is around 13-14 years on average (10-15 years) in reality long-term pairs only have 3-4 years disparity.

```{r age-gap , echo = FALSE}
age.diff <- age.difference.subgroup %>%
  filter(age - age_o >= 0) %>%
  mutate(n.years = age - age_o) %>%
  group_by(n.years) %>%
  summarise(
    n.matches = sum(n.matches)
  ) %>%
  arrange(n.years)

ggplot(age.diff[age.diff$n.years < 15,], aes(x = n.years, y = n.matches)) +
  geom_bar(stat = "identity", position = "dodge", fill="darkgreen") +
  xlab("Years of difference between people's age") + 
  ylab("Matches") + 
  ggtitle("Age factor in matching")
```

In speeddating people wants to choose a partner without huge age-gap.
As we can see in graph, most of relations is matched in between 0 and 5 age gap.

# Thanks
This is a exploratory data anlysis lecture assignment project. So for all team members it is first time making a analysis with R. During this process many shared analysis helped us about analyse methodolies and R syntax.

Very thanks to [JPHwang] (https://www.kaggle.com/jph84562/d/annavictoria/speed-dating-experiment/the-ugly-truth-of-people-decisions-in-speed-dating/notebook) for inspiring analysis for our team.   

Very thanks to [ColinLeverger] (https://www.kaggle.com/colinleverger/d/annavictoria/speed-dating-experiment/exploring-the-speed-dating-dataset) for useful analysing methods.  
